Evaluation

### 2019-10-31 evaluation.Rmd
tidying up the website markdowns
more website edits
more website updates
Website updates (#319)
* tidying up the website markdowns

* more website edits

* more website updates

* website edits

* Update report.Rmd

* Update about.md

* Update about.md
hide plotting in rmds

@@

```{r recent_eval, echo=FALSE, fig.width=10, fig.height=10}
plot_err_lead_spp_mods()
```

@@

```{r, hindcast_eval, echo=FALSE, fig.width=9, fig.height=15}
plot_cov_RMSE_mod_spp()
```

>>>>

Here we evaluate how each of the models has done compared to observed values.

<br>

@@

```{r, recent_eval, echo=FALSE, fig.width=10, fig.height=10}
#plot_err_lead_spp_mods()
```

<br>

@@

```{r, hindcast_eval, echo=FALSE, fig.width=9, fig.height=15}
#plot_cov_RMSE_mod_spp()
```
